---
title: "3340 Project"
author: "Jacob, Chris, Cali"
due date: "December 11th 2020"
output: html_document
---

We would like to answer the following research question: What is the relationship between the obesity rates, geographical region, and income across the 4 regions in the United States?

```{r setup, include=FALSE}
rm(list = ls())
setwd("C:\\Users\\calip\\Desktop\\Stat3340\\Project")
library(dplyr)
library(tidyverse)
read.csv("C:\\Users\\calip\\Desktop\\Stat3340\\Project\\original_data.csv") -> original_data
```

This first chunk of code allows us to set our working directory as well upload our csv file into R for analysis. We are using the libraries dplyr and tidyverse. These packages allow us to manipulate our data  as well run it faster and easier. 

```{r}
filter(original_data, Data_Value_Footnote != "Data not available because sample size is insufficient.") -> df_1
filter(df_1, Data_Value_Footnote != "Data not available because sample size is insufficient.  If data only missing for the confidence interval, the confidence interval was not calculated.") -> df_2

subset(df_2, select = -c(
  YearEnd, LocationAbbr, Datasource, Class, Data_Value_Unit,     Data_Value_Type, Data_Value_Alt, Data_Value_Footnote,   DataValueTypeID, StratificationCategoryId1, StratificationID1, ClassID, TopicID, QuestionID)) -> df_3
filter(df_3, LocationID < 59) -> df_4
```

In this section of code, we are removing the unnecessary data entries ("Data not available...") Since the data is not available, it will be insignificant to our data analysis.We are also removing irrelevant data columns as well removing US territories since it is not included in the US census map. 

```{r}
add_case(df_4, 
YearStart = 2012, LocationDesc = "Alabama", Topic = "Obesity / Weight Status", Question = "Percent of adults aged 18 years and older who have obesity", Data_Value = 29.999, Data_Value_Footnote_Symbol = "", Low_Confidence_Limit = 23.999, High_Confidence_Limit = 33.499, Sample_Size = 1255, Total = "", Age.years. = "", Education = "", Gender = "", Income = "", Race.Ethnicity = "Asian", GeoLocation = "(32.84057112200048, -86.63186076199969)", LocationID = 1, StratificationCategory1 = "Race/Ethnicity", Stratification1 = "Asian"         
         ) -> df_5
filter(df_5, Income != "Data not reported") -> df
df["311", "Sample_Size"] <- 1974
```

The lines above are very important for our data analysis. We are adding an additional data point to ensure that our dataset is unique when compared to other groups that have the same data. We also decided to add this data point specifically because ___Jake add your reasoning here___
